A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2019-12-08 paper.Rmd
Fixes #51
add author affiliations and resolve #101

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility
output:
  bookdown::pdf_document2:
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \linespread{2} 
  - \usepackage[utf8]{inputenc}
---

@@

In contrast to "raw data", "analysis ready data" should be in an easily readable plain-text format, such as comma-, tab- or semicolon-separated. Binary or proprietary formats are discouraged in favor of interoperability, as it requires special software to read, even if it is sometimes slower to read in and out, and harder to share due to size. There are times where Tidy Data format can inflate the size of data due to repetition, which make it difficult to share - in these cases it might be worthwhile to consider multiple smaller, connected tables or other easily compressible formats such as apache Arrow.

@@

Unlike CRAN, bioconductor, does not have a 5 megabyte limit for package size. They have a strict specification for how to organise genomic data in a package, so they can be used for data analysis out of the box. This is a robust solution, but only works for homogeneous data as found with bioinformatics. For example, data in their ExperimentData section (bioconductor.org/packages/3.9/data/experiment) can be used in a reliable way. However, such a strict standard would be impossible to enforce or scale on a repository as heterogeneous as CRAN.

>>>>

---
title: A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.
author: Nicholas J Tierney^1,2,*^, Karthik Ram^3,*^
output:
  bookdown::pdf_document2:
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \linespread{2} 
  - \usepackage[utf8]{inputenc}
---

1 = Monash University, Department of Econometrics and Business Statistics
2 = Australia Centre of Excellence for Mathematical and Statistical Frontiers
3 = University of California, Berkeley
* = Both authors contributed equally to the work

@@

In contrast to "raw data", "analysis ready data" should be in an easily readable plain-text format, such as comma-, tab- or semicolon-separated files. These typically have file extensions like `.csv`, `.tsv` or `.txt`. Binary or proprietary formats are discouraged in favor of interoperability, as it requires special software to read, even if it is sometimes slower to read in and out, and harder to share due to size. For example, R data formats like `.rds`, `.rda`, or SPSS, STATA, or SAS data formats, `.sav`, `.dta`, or `.sas7bdat`.

@@

Unlike CRAN, bioconductor, does not have a 5 megabyte limit for package size and offers a more liberal data inclusion policy. They have a strict specification for how to organise genomic data in a package, so they can be used for data analysis out of the box. This is a robust solution, but only works for homogeneous data as found with bioinformatics. For example, data in their ExperimentData section (bioconductor.org/packages/3.9/data/experiment) can be used in a reliable way. However, such a strict standard would be impossible to enforce or scale on a repository as heterogeneous as CRAN.
